---
title: "HealthCareAI"
author: "Parinitha Kompala"
date: "8/26/2021"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading library}
library(healthcareai)
```
analysing the pima data

```{r }
pima_diabetes #inbuit dataframe
dim(pima_diabetes)
summary(pima_diabetes)
```
```{r }
str(pima_diabetes)
```
Machine learing models
model 1-
```{r }
head(pima_diabetes)
names(pima_diabetes)

quick_models <- machine_learn(pima_diabetes, patient_id, outcome = diabetes)
quick_models
predictions <- predict(quick_models)
predictions
plot(predictions)
```
plotting the output od prediction 1
```{r }
plot(predictions)
```
prediction2-
```{r}
a_quick_models <- machine_learn(pima_diabetes, plasma_glucose, outcome = diabetes)
a_quick_models
a_predictions <- predict(quick_models)
a_predictions
```
plot of prediction2
```{r}
plot(a_predictions)
```
```{r }
quick_models %>%
  predict(outcome_groups = 2) %>%
  plot()
```
```{r }
a_quick_models %>%
  predict(outcome_groups = 2) %>%
  plot()
```
Doing some data profiling
```{}
missingness(pima_diabetes)
missingness(pima_diabetes) %>%
  plot()
```
Data preparation
```{r }
prep_data
split_data <- split_train_test(d = pima_diabetes,
                               outcome = diabetes,
                               p = .9,
                               seed = 84105)
prepped_training_data <- prep_data(split_data$train, patient_id, outcome = diabetes,
                                   center = TRUE, scale = TRUE,
                                   collapse_rare_factors = FALSE)
```
Data training 
```{r }
models <- tune_models(d = prepped_training_data,
                      outcome = diabetes,
                      tune_depth = 25,
                      metric = "PR")
evaluate(models, all_models = TRUE)
models["Random Forest"] %>%
  plot()
```
faster madel traing
```{r }
untuned_rf <- flash_models(d = prepped_training_data,
                           outcome = diabetes,
                           models = "RF",
                           metric = "PR")
```
Model interpretations
```{r }
interpret(models) %>%
  plot()
```
Variable importance
```{r }
get_variable_importance(models) %>%
  plot()
```
Exploring the data 
```{r}
explore(models) %>%
  plot()
```
Prediction
```{r}
predict(models)
test_predictions <-
  predict(models,
          split_data$test,
          risk_groups = c(low = 30, moderate = 40, high = 20, extreme = 10)
  )
```

```{r}
plot(test_predictions)
```
Saving Moving Loading models
```{r}
save_models(models, file = "my_models.RDS")
models <- load_models("my_models.RDS")
```

```{r}
regression_models <- machine_learn(pima_diabetes, patient_id, outcome = age)
summary(regression_models)
```
Regretion model
2.
```{r}
a_regression_models <- machine_learn(pima_diabetes, pregnancies, outcome = age)
summary(a_regression_models)
```

#prediction on a hypothetical new patient 1
```{r}
new_patient <- data.frame(
  pregnancies = 0,
  plasma_glucose = 80,
  diastolic_bp = 55,
  skinfold = 24,
  insulin = NA,
  weight_class = "???",
  pedigree = .2,
  diabetes = "N")
predict(regression_models, new_patient)
```
#prediction on a hypothetical new patient 2
```{r}
new_patient_2 <- data.frame(
  pregnancies = 3,
  plasma_glucose = 130,
  diastolic_bp = 60,
  skinfold = 24,
  insulin = NA,
  weight_class = "???",
  pedigree = .2,
  diabetes = "N")
predict(regression_models, new_patient_2)
```
